Evaluation of Types

### 2020-05-16 evaluation/R/evaluate-type-analysis.Rmd
Fix graph theme

@@

(union_frequency_folded %>%
ggplot(aes(alternative_count, percentage)) +
geom_col() +
scale_y_continuous(sec.axis = sec_axis(~ . * total_parameter_count, labels = count_labels), labels = relative_labels) +
labs(x="Types", y="Parameters") +
scale_x_discrete(limits=c("> 3", 3, 2, 1)) +
coord_flip() +
theme(legend.title = element_blank(), legend.position = "top")) %>%
save_graph("union_frequency.pdf")

>>>>

old_theme <- theme_set(theme_bw() + theme(text = element_text(size = 15), panel.border = element_blank()))

@@

(union_frequency_folded %>%
ggplot(aes(alternative_count, percentage)) +
geom_col() +
scale_y_continuous(sec.axis = sec_axis(~ . * total_parameter_count, labels = count_labels), labels = relative_labels) +
labs(x="Types", y="Positions") +
scale_x_discrete(limits=c("> 3", 3, 2, 1)) +
coord_flip() +
theme(legend.title = element_blank(), legend.position = "top")) %>%
save_graph("union_frequency.pdf")
